Requantization of time-dependent mean field for pairing collective motion in superfluid nuclei

### 2018-12-10 thesis/thesis.tex
thesis

\title{Requantization of time-dependent mean field
 for pairing collective motion in superfluid nuclei}
\author{Fang Ni}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\maketitle

\chapter*{Absract}

In most of nuclei, the structure of low-lying excited $0^+$ states, which had been called as $\beta$ vibration or two-phonon excitation, are complicate and mysterious from plenty of recent experimental data. The common suggestion from those experimentalists is that the pairing correlation plays an important role in such excited $0^+$ states because they found strange cross sections of two-nucleon transfer reactions. From theoretical viewpoint, excited $0^+$ states correspond to pairing vibrational mode, the elementary mode of excitation of pairing collective motions, in superfluid nuclei. 
Because quantum fluctuation is large in low-lying region, To understand such excited $0^+$ states, extend to the large-amplitude regime, but also pairing correlation.

\pagenumbering{roman}
\tableofcontents
\thispagestyle{empty}

@@

We introduce the pairing model in this chapter. The Hamiltonian of pairing model is
\begin{align}
	H &= \sum_{l=1}^L \epsilon_l n_l - g \sum_{l,l'} S_l^+ S_{l'}^- ,
\end{align}
where
\begin{align}
	n_l &= \sum_m a^{\dag}_{lm}a_{lm} \\
        S_l^{+} &= \sum_{m>0}a_{lm}^{\dag}a_{l\overline{m}}^{\dag} ,
\quad   S_l^{-} = S_l^{+\dag} .
\label{S_+}
\end{align}
In $L$ single-particle level system, each single-particle energy $\epsilon_l$ possesses $(2\Omega_l)$-fold
degeneracy ($\Omega_l=j_l+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$ and $\Omega_l-1/2$. $\overline{m}$ indicates the time reversal quantum number with respect to $m$. The strength of pairing correlation is represented by coupling constant $g$. We also define a seniority $\nu_l$, which is the number of unpaired particles in each level. The total number of unpaired particles is $\nu=\sum_l\nu_l$. The unpaired particles have no pairing interaction, and play a part in Pauli blocking effect.\par
In one-level system ($L=1$), the pairing dynamics is well understood. The analytic solution of the total energy is
\begin{align}
	E_{\nu}(N) = \epsilon N - \frac{1}{4}g(N-\nu)(2\Omega-N-\nu+2) .
	\label{onelevel}
\end{align}
The pairing rotational band created by the pairing correlation is completely parabolic with the pairing-rotational moment of inertia $2/g$. Also, the excited states in a specified $N$ is only described by the quantum number $\nu$. For example, the first excited state in even particle system is $\nu=2$ state, which correspond to one $J^{\pi}=0^+$ pair broken state.\par
The non-explicit dynamics arises in multi-level pairing model ($L\ge 2$). The pairing rotational mode includes higher order terms of $N$ due to the shell effect. In addition, several pairing vibrational modes emerge. The pairing vibration is not single particle motion specified by $\nu_l$, but a collective motion arisen from $J^{\pi}=0^+$ pairs. In order to solve the multi-level pairing Hamiltonian, we explain the numerical exact solution. Also, we derive the TDHFB equation to study the mean-field picture of pairing collective motions.

@@

\subsection{Diagonalization in quasispin space}
We introduce SU(2) quasispin operators fulfilling the follows commutation relation
\begin{equation}
  [S_l^0,S_{l'}^{+}] = \delta_{ll'}S_{l}^{+},\hspace{20pt}[S_{l}^{+},S_{l'}^{-}] = 2\delta_{ll'}S_{l}^{0}. 
  \label{SU2commu}
\end{equation}
If we set 
\begin{align}
  S_l^0 &= \frac{1}{2}(\sum_ma_{lm}^{\dag}a_{lm}-\Omega_l)
  \label{S_0}
\end{align}
and $S_l^+, S_l^-$ as in (\ref{S_+}), the commutation relation (\ref{SU2commu}) is fulfilled. Using quasispin operators, the Hamiltonian can be represented by quasispin operators
\begin{align}
	H &= \sum_l \epsilon_l (2S_l^0+\Omega_l) - g \sum_{l,l'} S_l^+ S_{l'}^- .
\end{align}
Therefore, any states $\ket{\psi}$ belong to SU(2)$\otimes\cdots\otimes$SU(2) Hilbert space, and can be expanded in the basis $\ket{S_1,S_1^0;\cdots;S_l,S_l^0;\cdots}$
\begin{equation}
  \ket{\psi} = \sum_{S_1^0,\cdots\,S_l^0,\cdots}c_{S_1^0,\cdots\,S_l^0,\cdots}\ket{S_1,S_1^0;\cdots;S_l,S_l^0;\cdots} .
\end{equation}

We consider the physical meaning of the quasispin space. Because $S_l^+$ and $S_l^-$ correspond to the creation and annihilation operators with respect to the $J^{\pi}=0^+$ pairs in each level, the quasispin space is decoupled from the space which the unpaired particles belong to. 
Also, $S_l^0$ is related to the occupation number in each level. $S_l^0=-S_l$ is the minimum value corresponding no $J^{\pi}=0^+$ pair in the level and $S_l^0=S_l$ is the maximum value corresponding full of $J^{\pi}=0^+$ pairs in the level. Because $\nu_l$ plays a part in Pauli blocking effect in the level, the absolute value of quasispin $S_l$ is
\begin{equation}
  S_l = \frac{1}{2}(\Omega_l-\nu_l).
\end{equation}

The dimension of the model space is $D=\prod_l(2S_l+1)$. However, $[H,N]=0$ indicates that the Hamiltonian is block diagonal with respect to the total particle number $N$. The model space can be reduced after we extract the combination of $\{S_l^0\}$ fulfilling
\begin{equation}
  N = \sum_l (2S_l^0+2S_l+\nu_l) .
\end{equation} 
For example, we consider the dimension of the single particle levels between the magic number 50 and 82. Under spherical symmetry, we have five single particle levels, $d_{5/2}$, $g_{7/2}$, $s_{1/2}$, $d_{3/2}$, and $h_{11/2}$. The corresponding degeneracy is $\{\Omega_l\}=\{3,4,1,2,6\}$. If we only consider the case for$\nu_l=0$, the dimension for the system is $D=840$. On the other hand, under a specified $N$, the dimensions are 105 for $N=14$ and 91 for $N=20$.

\subsection{Richardson equation}
As mentioned above, diagonalizing the Hamiltonian is simple method to obtain the exact solution.
However, diagonalization is time consuming when the model space becomes large. The calculation time is proportional to the cubes of the dimension of the model space. For example, there are 16 single particle levels between the magic number 50 and 82 in deformed nuclei. Because the dimension for the system is $D=2^{16}=65536$, the calculation time in deformed system is $\sim 10^5$ times as much as the case in spherical system. \par
The alternative method to obtain the exact solution is to solve Richardson equation. The idea was introduced by R. W. Richardson \cite{Richardson1, Richardson2, Richardson3, Richardson4, Richardson5}. We divide the total energy into two parts
\begin{align}
  E &= \braket{\psi|H|\psi} \\
  &= \sum_l \epsilon_l \nu_l + \sum_{\alpha=1}^M E_{\alpha} .
\end{align}
The first term is the energy of unpaired particle, and the second term is the total energy of $J^{\pi}=0^+$ pairs. The pair-energy $E_{\alpha}$ is derived from the non-linear equations
\begin{equation}
  1 - g\sum_l \frac{\Omega_l-\nu_l}{2\epsilon_l-E_{\alpha}} + 2g\sum_{\beta(\neq\alpha)}^M \frac{1}{E_{\beta}-E_{\alpha}} = 0 .
\end{equation}
$M$ indicates the number of $J^{\pi}=0^+$ pairs in the system, and equals to the numbers of the non-linear equations. $E_{\alpha}$ can become not only real numbers, but also complex conjugate pairs when $M\ge 2$.

We solved the non-linear equations numerically in general. If we input a set of initial values $E_{\alpha}^{0}$ into the equations, the values will converge by using proper numerical algorithm such as Newton-Raphson method. The difficult point is that we cannot directly specify the number of excitation from the obtained excitation energy because the converged excitation energy $\sum_{\alpha=1}^M E_{\alpha}$ can be any number of excitation. To specify the number of excitation, we can use the idea in Ref. \cite{Richardson4}, which discussed the behavior of the $E_{\alpha}$ as a function of $g$ for ground and each low-lying excitation energy.

The eigenvalues can be also calculated numerically by using the obtained $E_{\alpha}$. Actually, we need to calculate the matrix elements for specific operators we interest (e.g. number operator, two-particle transition operator), without obtaining the explicit eigenvectors. For example, the occupation number can be obtained in the following non-linear equations
\begin{align}
n.
\end{align}
%However, the equation

\section{TDHFB dynamics}
%In realistic nuclear system with nuclear effective interaction, the necessary model space is huge. To diagonalize the effective Hamiltonian is extremely difficult task. Such study is done by shell model calculation. In alternative way, we only prepare a limited model space, which supposed to be reproduce the important parts of nuclear properties. The time-dependent mean-field theory 
We apply time-dependent mean-field (TDMF) theory to examine the classical picture of the pairing dynamics. With pairing correlation, TDMF theory attributes to TDHFB theory.
The TDHFB equation can be derived from the time-dependent variational principle,
\begin{equation}
  \delta\mathcal{S}=0, \quad 
  \mathcal{S} \equiv \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt ,
  \label{variation}
\end{equation}
where $\ket{\phi(t)}$ is the time-dependent generalized Slater determinant (coherent state) obtained from Thouless' theorem
\begin{equation}
  \ket{\phi(t)} = \mathcal{R}\exp{\left( \sum_{k<k'}Z_{kk'}(t)\beta_k^{\dag}\beta_{k'}^{\dag}
    \right)}\ket{\Phi_0} .
\end{equation}
$\beta_k^{\dag}$ is quasiparticle creation operator and $\mathcal{R}$ is normalization factor. $\ket{\Phi_0}$ is generally chosen as ground state or vacuum state. $Z_{kk'}(t)$ is time-dependent complex number determined by TDHFB equation.

\subsection{Hamilton's equation}
We derive the TDHFB equation in pairing model. First, we consider the time-dependent coherent state. Because the noticeable phenomenon is the dynamics for $J^{\pi}=0^+$ pairs in pairing model, we can describe the time-dependent coherent state in SU(2) quasispin space. Using Thouless' theorem, the time-dependent coherent state becomes
\begin{equation}
	\ket{Z(t)} = \prod_{l} \left(1+|Z_l(t)|^2\right)^{-S_l}
	\exp [Z_l(t) S_l^{+}] \ket{0} .
 \label{coherent}
\end{equation}
Here, we choose $\ket{\Phi_0}=\ket{0}$ which is vacuum (zero particle) state. In the quasispin representation, $\ket{0}=\prod_l \ket{S_l,-S_l}$. The coherent state is the extension of BCS trail wave function, which consists of the superposition of different particle number states. $Z_l$ are complex numbers. $|Z_l|=0$ corresponds to empty occupation and $|Z_l|=\infty$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.\par
 With the transformation $Z_l = \tan{\frac{\theta_l}{2}}e^{-i\chi_l}$ ($0\leq\theta\leq\pi$, $0\leq\chi<2\pi$), the Lagrangian and the expectation value of Hamiltonian become
\begin{align}
	\mathcal{L}(t) =& \braket{Z(t)|i\hbar\frac{\partial}{\partial t}-H|Z(t)}
	=\sum_l j_l\dot{\chi_l} - \mathcal{H}(\chi,j) ,\\
	\mathcal{H}(\chi,j) \equiv& \braket{Z(t)|H|Z(t)} \nonumber \\
	=& \sum_l \epsilon_l\nu_l + \sum_l 2\epsilon_lj_l - g\sum_l \left( (\Omega_l-\nu_l) j_l - j_l^2 +\frac{j_l^2}{\Omega_l-\nu_l} \right) \nonumber \\
	&- 2g\sum_{l_1<l_2} \sqrt{j_{l_1}j_{l_2}(\Omega_{l_1}-\nu_{l_1}-j_{l_1})(\Omega_{l_2}-\nu_{l_2}-j_{l_2})}\cos{(\chi_{l_1}-\chi_{l_2})}   ,
	\label{Hamiltonian}
\end{align}
where $\chi_l$ are the canonical coordinates and $j_l$ are the conjugate momenta defined in
\begin{align}
  j_l\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_l}=S_l(1-\cos{\theta}_l) .
  \label{momenta}
\end{align}
The detailed derivations are written in Appendix \ref{derivation}. The canonical variables $(\chi,j)$ have clear physical meaning. $\chi_l$ represent a kind of gauge angle of each level, and $j_l$ correspond to the occupation number of each level
\begin{align}
  \braket{Z|n_l|Z} = \nu_l + 2j_l .
  \label{occ}
\end{align}
From (\ref{momenta}), we can find that $0\le j_l\le 2S_l$, where $j_l=0$ corresponds to empty occupation and $j_l=2S_l$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.
Using canonical variables, the TDHFB equations attribute to the Hamilton's equations
\begin{equation}
	\dot{\chi_l} = \frac{\partial\mathcal{H}}{\partial j_l}, \quad
	\dot{j_l} = -\frac{\partial\mathcal{H}}{\partial \chi_l} .
\end{equation}

\subsection{Constant of motion}
\label{constant}
The number of the TDHFB degrees of freedom is same as the number of the single-particle levels. However, there is one constant of motion, pairing rotation. Using (\ref{occ}), the total particle number can be written in
\begin{align}
	N = \braket{Z|\hat{N}|Z} = \nu + 2J ,
\end{align}
where $J$ is defined in
\begin{align}
	J \equiv \sum_l j_l .
\end{align}
Because $\nu$ is nothing but quantum number, the total particle number can be specified by $J$.
We can confirm that the total particle number is conserved by checking the Poisson Bracket
\begin{align}
	\{\mathcal{H},J\}_{PB} &= \sum_l \left(
	\frac{\partial\mathcal{H}}{\partial\chi_l}\frac{\partial J}{\partial j_l}
	- \frac{\partial\mathcal{H}}{\partial j_l}\frac{\partial J}{\partial \chi_l} \right) \nonumber \\
	&= \sum_l \frac{\partial\mathcal{H}}{\partial\chi_l} \nonumber \\
	&= \sum_l 2g \sum_{l'\neq l} \sqrt{j_{l}j_{l'}(\Omega_{l}-\nu_{l}-j_{l})(\Omega_{l'}-\nu_{l'}-j_{l'})}\sin{(\chi_{l}-\chi_{l'})} \nonumber \\
	&= 0 .
\end{align} 
Actually, $J$ correspond to a conjugate momentum with respect to a global gauge angle $\Phi$. We note that $\Phi$ is not necessarily becoming $\Phi=\sum_l \chi_l/L$ because the explicit form of $\Phi$ depends on the coordinate transformation. In other words, the condition of total particle number conservation cannot determine the form of $\Phi$ uniquely.

The canonical variable $(\Phi,J)$ describes the pairing rotation. The pairing rotational band emerges in the particle number chain ($\cdots,N-2,N,N+2,\cdots$). The last term in (\ref{Hamiltonian}) contains the higher order terms with respect to $N$. It related to the shell effect. In single-level system, the last term in (\ref{Hamiltonian}) disappears and (\ref{Hamiltonian}) attributes to (\ref{onelevel}). The pairing rotational band is exactly parabolic. In multi-level system, the coupling constant $g$ and single-particle energy $\epsilon_l$ affects significantly to the last term in (\ref{Hamiltonian}). The parabolic structure will be broken when the shell effect is strong.

>>>>

\begin{document}
\begin{titlepage}
\begin{center}
\vspace*{100truept}
{\huge Requantization of time-dependent mean field}\\
\vspace{5truept}
{\huge for pairing collective motion in superfluid nuclei}\\
\vspace*{120truept}
{\LARGE Fang Ni}\\
\vspace*{280truept}
{\LARGE February 2019}\\ 
\end{center}
\end{titlepage} 
\newpage

\thispagestyle{empty}
\newpage

\begin{titlepage}
\begin{center}
\vspace*{100truept}
{\huge Requantization of time-dependent mean field}\\
\vspace{5truept}
{\huge for pairing collective motion in superfluid nuclei}\\
\vspace*{120truept}
{\LARGE Fang Ni}\\
\vspace{5truept}
{\LARGE Doctral Program in Physics}\\
\vspace*{200truept}
{\LARGE Submitted to the Graduate School of}\\
\vspace{5truept}
{\LARGE Pure and Applied Sciences}\\
\vspace{5truept}
{\LARGE in Partial Fulfillment of the Requirements} \\
\vspace{5truept}
{\LARGE for the Degree of Doctor of Philosophy in}\\
\vspace{5truept}
{\LARGE Science}\\
\vspace*{15truept}
{\LARGE at the}\\
\vspace{5truept}
{\LARGE University of Tsukuba}\\ 
\end{center}
\end{titlepage} 
\thispagestyle{empty}

\chapter*{Abstract}
\thispagestyle{empty}

In most of nuclei, the structure of low-lying excited $0^+$ states, which had been called as $\beta$ vibration or two-phonon excitation, are complicate and mysterious from plenty of recent experimental data. The common suggestion from those experimentalists is that the pairing correlation plays an important role in such excited $0^+$ states because they found strange cross sections of two-nucleon transfer reactions. From theoretical viewpoint, 
%excited $0^+$ states in superfluid nuclei correspond to not only quadrupole vibrational mode, the elementary mode of excitation of quadrupole collective motions, but also pairing vibrational mode, the elementary mode of excitation of pairing collective motions. 
the competition between quadrupole correlation and pairing correlation causes complicate structure of low-lying excited $0^+$ states. 
We aim to understand such excited $0^+$ states based on time-dependent mean-field (TDMF) theory. Because quantum fluctuation is large in low-lying excitation region, theoretical framework in large-amplitude regime is necessary. However, the theoretical framework to describe pairing collective motions in large-amplitude regime is not developed. The nature of pairing collective motions in low-lying excitation region is still unclear.

We consider the theoretical framework to describe large-amplitude collective motions associated with nuclear pairing. In general, the low-lying excited states can be obtained in two steps: (1) solve TDMF equation to obtain classical trajectories; (2) quantize such classical trajectories to obtain the excited states. The step 2 is called ``requantization''. In this thesis, we focus on step 2 and discuss the requantization method in detail. To simplify the system, apart from realistic nuclear system, we consider the pairing collective motions in multi-level pairing model. We divide the pairing system into two classes, integrable system and non-integrable system. The former one corresponds to two-level system and the later one corresponds to the system more than three-level. Because the description of requantization is different between the two, we consider the requantization methods for each case, respectively.

In integrable system, the requantization of TDMF is particular feasible because we can easily find the periodic orbits. We apply three different requantization methods, canonical quantization, Fourier decomposition of the time-dependent observables, and stationary phase approximation (SPA) to the path integral. Comparing each requantization method with exact solution in various two-level system, respectively, SPA turns out to be most accurate between the three and can describe the excited states quantitatively, especially for the calculation of two-particle transition strength. Because the requantized wave functions from SPA are given in terms of the microscopic degrees of freedom, the transition matrix elements can be calculated directly.

Actually, SPA cannot be applied to non-integrable system straightforwardly because finding the periodic orbits is extremely difficult task. We propose a new theoretical approach which enables SPA to apply to non-integrable system, namely, combining SPA with adiabatic self-consistent collective coordinate (ASCC) method (ASCC+SPA). The concept is that we employ ASCC to extract an integrable subspace from TDMF phase space, and apply SPA to obtain the excited states. The detailed derivation is shown in the text.
From the application to the low-lying excited $0^+$ states in three-level system and Pb isotopes system, we find ASCC+SPA gives a reasonable description.

We also examine the performance of the pairing collective model which phenomenologically assumes pairing gap parameter and gauge angle as collective coordinates. We check the one-to-one correspondence between the collective coordinates from TDMF dynamics itself and those in collective model. We find the collective coordinate describing pairing vibration has no one-to-one correspondence between the two, in both integrable and non-integrable system. The applicability of the collective model is limited for the nuclear pairing.

We summarize the achievements in this thesis. We find a reasonable requantization method, SPA, from the study in integrable system. Using SPA, we construct a theoretical framework of ASCC+SPA to requantize the pairing collective motions in non-integrable system. Also, we demonstrate that to describe pairing vibration properly, it is necessary to employ the collective coordinate extracted from TDMF degrees of freedom itself, instead of the phenomenological collective coordinate, pairing gap parameter. With the development of computational power, we think 
ASCC+SPA is promising tool to elucidate the structure of mysterious low-lying excited $0^+$ states in nuclei.

\thispagestyle{empty}

\pagenumbering{roman}
\setcounter{page}{-1}
\tableofcontents
%\thispagestyle{empty}

@@

We introduce the pairing model in this chapter. The Hamiltonian of pairing model is
\begin{align}
	H &= \sum_{\alpha=1}^L \epsilon_{\alpha} n_{\alpha} - g \sum_{\alpha\beta} S_{\alpha}^+ S_{\beta}^- ,
\end{align}
where
\begin{align}
	n_{\alpha} &= \sum_m a^{\dag}_{j_\alpha m}a_{j_\alpha m} \\
        S_{\alpha}^{+} &= \sum_{m>0}a_{j_\alpha m}^{\dag}a_{j_\alpha \overline{m}}^{\dag} ,
\quad   S_{\alpha}^{-} = S_{\alpha}^{+\dag} .
\label{S_+}
\end{align}
In $L$ single-particle level system, each single-particle energy $\epsilon_{\alpha}$ possesses $(2\Omega_{\alpha})$-fold
degeneracy ($\Omega_{\alpha}=j_{\alpha}+1/2$)
and $\sum_{m>0}$ indicates the summation over $m=1/2,3/2,\cdots,$ and $\Omega_{\alpha}-1/2$. $\overline{m}$ indicates the time reversal quantum number with respect to $m$. The strength of pairing correlation is represented by coupling constant $g$. We also define a seniority $\nu_{\alpha}$, which is the number of unpaired particles in each level. The total number of unpaired particles is $\nu=\sum_{\alpha}\nu_{\alpha}$. The unpaired particles have no pairing interaction, and play a part in Pauli blocking effect.\par
In one-level system ($L=1$), the pairing dynamics is well understood. The analytic solution of the total energy is
\begin{align}
	E_{\nu}(N) = \epsilon N - \frac{1}{4}g(N-\nu)(2\Omega-N-\nu+2) .
	\label{onelevel}
\end{align}
The pairing rotational band created by the pairing correlation is completely parabolic with the pairing-rotational moment of inertia $2/g$. Also, the excited states in a specified $N$ is only described by the quantum number $\nu$. For example, the first excited state in even particle system is $\nu=2$ state, which correspond to one $J^{\pi}=0^+$ pair broken state.\par
The non-explicit dynamics arises in multi-level pairing model ($L\ge 2$). The pairing rotational mode includes higher order terms of $N$ due to the shell effect. In addition, several pairing vibrational modes emerge. The pairing vibration is not single particle motion specified by $\nu_{\alpha}$, but a collective motion arisen from $J^{\pi}=0^+$ pairs. In order to solve the multi-level pairing Hamiltonian, we explain the numerical exact solution. Also, we derive the TDHFB equation to study the mean-field picture of pairing collective motions.

@@

\subsection{Diagonalization in quasispin space}
We introduce SU(2) quasispin operators fulfilling the follows commutation relation
\begin{equation}
  [S_{\alpha}^0,S_{\beta}^{+}] = \delta_{\alpha\beta}S_{\alpha}^{+},\hspace{20pt}[S_{\alpha}^{+},S_{\beta}^{-}] = 2\delta_{\alpha\beta}S_{\alpha}^{0}. 
  \label{SU2commu}
\end{equation}
If we set 
\begin{align}
  S_{\alpha}^0 &= \frac{1}{2}(\sum_ma_{j_\alpha m}^{\dag}a_{j_\alpha m}-\Omega_{\alpha})
  \label{S_0}
\end{align}
and $S_{\alpha}^+, S_{\alpha}^-$ as in (\ref{S_+}), the commutation relation (\ref{SU2commu}) is fulfilled. Using quasispin operators, the Hamiltonian can be represented by quasispin operators
\begin{align}
	H &= \sum_{\alpha} \epsilon_{\alpha} (2S_{\alpha}^0+\Omega_{\alpha}) - g \sum_{\alpha\beta} S_{\alpha}^+ S_{\beta}^- .
\end{align}
Therefore, any states $\ket{\psi}$ belong to SU(2)$\otimes\cdots\otimes$SU(2) Hilbert space, and can be expanded in the basis $\ket{S_1,S_1^0;\cdots;S_{\alpha},S_{\alpha}^0;\cdots}$
\begin{equation}
  \ket{\psi} = \sum_{S_1^0,\cdots\,S_{\alpha}^0,\cdots}c_{S_1^0,\cdots\,S_{\alpha}^0,\cdots}\ket{S_1,S_1^0;\cdots;S_{\alpha},S_{\alpha}^0;\cdots} .
\end{equation}

We consider the physical meaning of the quasispin space. Because $S_{\alpha}^+$ and $S_{\alpha}^-$ correspond to the creation and annihilation operators with respect to the $J^{\pi}=0^+$ pairs in each level, the quasispin space is decoupled from the space which the unpaired particles belong to. 
Also, $S_{\alpha}^0$ is related to the occupation number in each level. $S_{\alpha}^0=-S_{\alpha}$ is the minimum value corresponding no $J^{\pi}=0^+$ pair in the level and $S_{\alpha}^0=S_{\alpha}$ is the maximum value corresponding full of $J^{\pi}=0^+$ pairs in the level. Because $\nu_{\alpha}$ plays a part in Pauli blocking effect in the level, the absolute value of quasispin $S_{\alpha}$ is
\begin{equation}
  S_{\alpha} = \frac{1}{2}(\Omega_{\alpha}-\nu_{\alpha}).
\end{equation}

The dimension of the model space is $D=\prod_{\alpha}(2S_{\alpha}+1)$. However, $[H,N]=0$ indicates that the Hamiltonian is block diagonal with respect to the total particle number $N$. The model space can be reduced after we extract the combination of $\{S_{\alpha}^0\}$ fulfilling
\begin{equation}
  N = \sum_{\alpha} (2S_{\alpha}^0+2S_{\alpha}+\nu_{\alpha}) .
\end{equation} 
For example, we consider the dimension of the single particle levels between the magic number 50 and 82. Under spherical symmetry, we have five single particle levels, $d_{5/2}$, $g_{7/2}$, $s_{1/2}$, $d_{3/2}$, and $h_{11/2}$. The corresponding degeneracy is $\{\Omega_{\alpha}\}=\{3,4,1,2,6\}$. If we only consider the case for$\nu_{\alpha}=0$, the dimension for the system is $D=840$. On the other hand, under a specified $N$, the dimensions are 105 for $N=14$ and 91 for $N=20$.

\subsection{Richardson equation}
As mentioned above, diagonalizing the Hamiltonian is simple method to obtain the exact solution.
However, diagonalization is time consuming when the model space becomes large. The calculation time is proportional to the cubes of the dimension of the model space. For example, there are 16 single particle levels between the magic number 50 and 82 in deformed nuclei. Because the dimension for the system is $D=2^{16}=65536$, the calculation time in deformed system is $\sim 10^5$ times as much as the case in spherical system. \par
The alternative method to obtain the exact solution is to solve Richardson equation. The idea was introduced by R. W. Richardson \cite{Richardson1, Richardson2, Richardson3, Richardson4, Richardson5}. We divide the total energy into two parts
\begin{align}
  E &= \braket{\psi|H|\psi} \\
  &= \sum_{\alpha} \epsilon_{\alpha} \nu_{\alpha} + \sum_{m=1}^M E_{m} .
\end{align}
The first term is the energy of unpaired particle, and the second term is the total energy of $J^{\pi}=0^+$ pairs. The pair-energy $E_{\alpha}$ is derived from the non-linear equations
\begin{equation}
  1 - g\sum_{\alpha} \frac{\Omega_{\alpha}-\nu_{\alpha}}{2\epsilon_{\alpha}-E_{\alpha}} + 2g\sum_{n(\neq m)}^M \frac{1}{E_{n}-E_{m}} = 0 .
\end{equation}
$M$ indicates the number of $J^{\pi}=0^+$ pairs in the system, and equals to the numbers of the non-linear equations. $E_{m}$ can become not only real numbers, but also complex conjugate pairs when $M\ge 2$.

We solved the non-linear equations numerically in general. If we input a set of initial values $E_{m}^{0}$ into the equations, the values will converge by using proper numerical algorithm such as Newton-Raphson method. The difficult point is that we cannot directly specify the number of excitation from the obtained excitation energy because the converged excitation energy $\sum_{m=1}^M E_{m}$ can be any number of excitation. To specify the number of excitation, we can use the idea in Ref. \cite{Richardson4}, which discussed the behavior of the $E_{m}$ as a function of $g$ for ground and each low-lying excitation energy.

The eigenvalues can be also calculated numerically by using the obtained $E_{m}$. Actually, we need to calculate the matrix elements for specific operators we interest (e.g. number operator, two-particle transition operator), without obtaining the explicit eigenvectors. For example, the occupation number can be obtained in the following non-linear equations
\begin{align}
n.
\end{align}
%However, the equation

\section{TDHFB dynamics}
\label{2-2}
%In realistic nuclear system with nuclear effective interaction, the necessary model space is huge. To diagonalize the effective Hamiltonian is extremely difficult task. Such study is done by shell model calculation. In alternative way, we only prepare a limited model space, which supposed to be reproduce the important parts of nuclear properties. The time-dependent mean-field theory 
We apply time-dependent mean-field (TDMF) theory to examine the classical picture of the pairing dynamics. With pairing correlation, TDMF theory attributes to TDHFB theory.
The TDHFB equation can be derived from the time-dependent variational principle,
\begin{equation}
  \delta\mathcal{S}=0, \quad 
  \mathcal{S} \equiv \int \braket{\phi(t)|i\frac{\partial}{\partial t}-H|\phi(t)}dt ,
  \label{variation}
\end{equation}
where $\ket{\phi(t)}$ is the time-dependent generalized Slater determinant (coherent state) obtained from Thouless' theorem
\begin{equation}
  \ket{\phi(t)} = \mathcal{R}\exp{\left( \sum_{k<k'}Z_{kk'}(t)\beta_k^{\dag}\beta_{k'}^{\dag}
    \right)}\ket{\Phi_0} .
\end{equation}
$\beta_k^{\dag}$ is quasiparticle creation operator and $\mathcal{R}$ is normalization factor. $\ket{\Phi_0}$ is generally chosen as ground state or vacuum state. $Z_{kk'}(t)$ is time-dependent complex number determined by TDHFB equation.

\subsection{Hamilton's equation}
We derive the TDHFB equation in pairing model. First, we consider the time-dependent coherent state. Because the noticeable phenomenon is the dynamics for $J^{\pi}=0^+$ pairs in pairing model, we can describe the time-dependent coherent state in SU(2) quasispin space. Using Thouless' theorem, the time-dependent coherent state becomes
\begin{equation}
	\ket{Z(t)} = \prod_{\alpha} \left(1+|Z_{\alpha}(t)|^2\right)^{-S_{\alpha}}
	\exp [Z_{\alpha}(t) S_{\alpha}^{+}] \ket{0} .
 \label{coherent}
\end{equation}
Here, we choose $\ket{\Phi_0}=\ket{0}$ which is vacuum (zero particle) state. In the quasispin representation, $\ket{0}=\prod_{\alpha} \ket{S_{\alpha},-S_{\alpha}}$. The coherent state is the extension of BCS trail wave function, which consists of the superposition of different particle number states. $Z_{\alpha}$ are complex numbers. $|Z_{\alpha}|=0$ corresponds to empty occupation and $|Z_{\alpha}|=\infty$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.\par
 With the transformation $Z_{\alpha} = \tan{\frac{\theta_{\alpha}}{2}}e^{-i\chi_{\alpha}}$ ($0\leq\theta\leq\pi$, $0\leq\chi<2\pi$), the Lagrangian and the expectation value of Hamiltonian become
\begin{align}
	\mathcal{L}(t) =& \braket{Z(t)|i\hbar\frac{\partial}{\partial t}-H|Z(t)}
	=\sum_{\alpha} j_{\alpha}\dot{\chi_{\alpha}} - \mathcal{H}(\chi,j) ,\\
	\mathcal{H}(\chi,j) \equiv& \braket{Z(t)|H|Z(t)} \nonumber \\
	=& \sum_{\alpha} \epsilon_{\alpha}\nu_{\alpha} + \sum_{\alpha} 2\epsilon_{\alpha}j_{\alpha} - g\sum_{\alpha} \left( (\Omega_{\alpha}-\nu_{\alpha}) j_{\alpha} - j_{\alpha}^2 +\frac{j_{\alpha}^2}{\Omega_{\alpha}-\nu_{\alpha}} \right) \nonumber \\
	&- 2g\sum_{\alpha<\beta} \sqrt{j_{\alpha}j_{\beta}(\Omega_{\alpha}-\nu_{\alpha}-j_{\alpha})(\Omega_{\beta}-\nu_{\beta}-j_{\beta})}\cos{(\chi_{\alpha}-\chi_{\beta})}   ,
	\label{Hamiltonian}
\end{align}
where $\chi_{\alpha}$ are the canonical coordinates and $j_{\alpha}$ are the conjugate momenta defined in
\begin{align}
  j_{\alpha}\equiv \frac{\partial\mathcal{L}}{\partial\dot{\chi}_{\alpha}}=S_{\alpha}(1-\cos{\theta}_{\alpha}) .
  \label{momenta}
\end{align}
The detailed derivations are written in Appendix \ref{derivation}. The canonical variables $(\chi,j)$ have clear physical meaning. $\chi_{\alpha}$ represent a kind of gauge angle of each level, and $j_{\alpha}$ correspond to the occupation number of each level
\begin{align}
  \braket{Z|n_{\alpha}|Z} = \nu_{\alpha} + 2j_{\alpha} .
  \label{occ}
\end{align}
From (\ref{momenta}), we can find that $0\le j_{\alpha}\le 2S_{\alpha}$, where $j_{\alpha}=0$ corresponds to empty occupation and $j_{\alpha}=2S_{\alpha}$ corresponds to full occupation for $J^{\pi}=0^+$ pairs.
Using canonical variables, the TDHFB equations attribute to the Hamilton's equations
\begin{equation}
	\dot{\chi_{\alpha}} = \frac{\partial\mathcal{H}}{\partial j_{\alpha}}, \quad
	\dot{j_{\alpha}} = -\frac{\partial\mathcal{H}}{\partial \chi_{\alpha}} .
\end{equation}
